% Common commands
\newcommand{ \logg} {$\log{g}$}
\newcommand{ \rsun }{$R_{\sun}$}
\newcommand{ \msun }{$M_{\sun}$}
\newcommand{ \lsun }{$L_{\sun}$}
\newcommand{ \rstar }{$R_{\star}$}
\newcommand{ \mstar}{$M_{\star}$}
\newcommand{ \tstar}{$T_{\star}$}
\newcommand{ \rp}{$R_{p}$}
\newcommand{ \massp}{$M_{p}$}
\newcommand{ \Splanet}{$S_{p}$}
\newcommand{ \teq}{T$_{\rm eq}$}
\newcommand{ \rj}{$R_{J}$}
\newcommand{ \mj}{$M_{J}$}
\newcommand{ \re}{$R_{\earth}$}
\newcommand{ \Rearth}{$R_{\earth}$}
\newcommand{ \me}{$M_{\earth}$}
\newcommand{ \se}{$S_{\earth}$}
\newcommand{ \kepler}{\emph{Kepler}}
\newcommand{ \KEPLER}{\emph{KEPLER}}
\newcommand{ \keplers}{\emph{Kepler's}}
\newcommand{ \Ktwo}{\emph{K2}}
%\newcommand{ \th}{$^{\rm th}$}
\newcommand{ \injtce}{injTCE}
\newcommand{ \scrtce}{scrTCE}
\newcommand{ \invtce}{invTCE}
\newcommand{ \opstce}{obsTCE}
\newcommand{ \injtces}{injTCEs}
\newcommand{ \scrtces}{scrTCEs}
\newcommand{ \invtces}{invTCEs}
\newcommand{ \opstces}{obsTCEs}

% Important numbers
\newcommand{ \ntces}{34,032}        % Number of DR25 TCEs, includes rogue
\newcommand{ \ntcesnorogue}{32,534}        % Number of DR25 TCEs, no rogue
\newcommand{ \npredrtwentyfourkois}{7,348}  % Number of KOIS pre-DR24.
\newcommand{ \npredrtwentyfivekois}{8,826}  % Number of KOIs pre-DR25
\newcommand{ \nkebs}{2,605}         % Number of EBWG True EBs used in ephem matching.
\newcommand{ \nephemmatch}{1,859}   % Number of TCEs ruled as FPs due to ephemeris matching in DR24.
\newcommand{ \nonlyephemmatch}{106} % Number of TCEs ruled as FPs ONLY due to ephemeris matching in DR24.
\newcommand{ \nscrtces}{13782} %number of scrambled TCEs after cleaning and no rogue (SET)
\newcommand{ \ninvtces}{14953} %number of inverted TCEs after cleaning and no rogue. (SET)
\newcommand{ \ninjtces}{45377} %number of injected and recovered TCEs, no rogue
\newcommand{ \ninjecttargs}{146,294} % number of targets that received an on-target planet transit injection
\newcommand{ \nkoisdr}{8054} %Number of KOIs in the DR25 catalog.

%For Authors
\newcommand{\nasa} {NASA Ames Research Center, Moffett Field, CA 94035, USA}
\newcommand{\seti}{SETI Institute, 189 Bernardo Ave, Suite 200, Mountain View, CA 94043, USA}
\newcommand{\stsci}{Space Telescope Science Institute, 3700 San Martin Drive, Baltimore, MD 21218}
\newcommand{\nexsci}{IPAC-NExScI, Mail Code 100-22, Caltech, 1200 E. California Blvd. Pasadena, CA 91125}
\newcommand{\mitadd}{MIT Kavli Institute for Astrophysics and Space Research, 77 Massachusetts Avenue, 37-241, Cambridge, MA 02139}
\newcommand{\orbital}{Orbital Insight, 100 W Evelyn Ave \#110, Mountain View, CA 94041}
\newcommand{\bishop}{Dept. of Physics and Astronomy, Bishop's University, 2600 College St., Sherbrooke, QC, J1M 1Z7, Canada}
\newcommand{\bari}{Bay Area Environmental Research Institute, 625 2nd St., Ste 209, Petaluma, CA 94952, USA}
\newcommand{\nsffellow}{NSF Astronomy \& Astrophysics Postdoctoral Fellow}
\newcommand{\cfa}{Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge MA 02138, USA}
\newcommand{\aarhus}{Stellar Astrophysics Centre, Dept. of Physics and Astronomy, Aarhus University, Ny Munkegade 120, 8000 Aarhus C, Denmark}
\newcommand{\nasagoddard}{NASA Goddard Space Flight Center, 8800 Greenbelt Road, Greenbelt, MD 20771}
\newcommand{\wyle}{KRBwyle, 2400 Nasa Parkway, Houston, TX 77058 USA}
\newcommand{\pennstate}{Dept. of Astronomy \& Astrophysics, 525 Davey Laboratory, The Pennsylvania State University, University Park, PA, 16802, USA} 
\newcommand{\habworlds}{Center for Exoplanets and Habitable Worlds, 525 Davey Laboratory, The Pennsylvania State University, University Park, PA, 16802, USA} 
%Command to Bold Changes, easy to turn off here
%\newcommand{\mybold}[1]{\textbf{#1}}

\lccode`1=`1
\lccode`2=`2
\lccode`3=`3

\hyphenation{obsTCE}   % Makes it so that "obsTCE" is never hyphenated to break a line
\hyphenation{invTCE}   % Makes it so that "invTCE" is never hyphenated to break a line
\hyphenation{scrTCE}   % Makes it so that "scrTCE" is never hyphenated to break a line
\hyphenation{scr1TCE}   % Makes it so that "scr1TCE" is never hyphenated to break a line
\hyphenation{injTCE}   % Makes it so that "injTCE" is never hyphenated to break a line
\hyphenation{inj1TCE}   % Makes it so that "inj1TCE" is never hyphenated to break a line
\hyphenation{inj2TCE}   % Makes it so that "inj2TCE" is never hyphenated to break a line
\hyphenation{inj3TCE}   % Makes it so that "inj3TCE" is never hyphenated to break a line

\hyphenation{obsTCEs}   % Makes it so that "obsTCEs" is never hyphenated to break a line
\hyphenation{invTCEs}   % Makes it so that "invTCEs" is never hyphenated to break a line
\hyphenation{scrTCEs}   % Makes it so that "scrTCEs" is never hyphenated to break a line
\hyphenation{scr1TCEs}   % Makes it so that "scr1TCEs" is never hyphenated to break a line
\hyphenation{injTCEs}   % Makes it so that "injTCEs" is never hyphenated to break a line
\hyphenation{inj1TCEs}   % Makes it so that "inj1TCEs" is never hyphenated to break a line
\hyphenation{inj2TCEs}   % Makes it so that "inj2TCEs" is never hyphenated to break a line
\hyphenation{inj3TCEs}   % Makes it so that "inj3TCEs" is never hyphenated to break a line



% using aastex version 6.1
%\documentclass[apj,twocolappendix,numberedappendix]{emulateapj}
\documentclass[twocolumn,tighten,trackchanges]{aastex61}
%,trackchanges
\setcounter{secnumdepth}{4}  % Required to get section headers like  4.1.2.1 as required by AAS journal style guide

\let\underscore\_
\renewcommand{\_}{\discretionary{\underscore}{}{\underscore}}  % This and the previous line lets the mnemonic flags gracefully line wrap


\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{url}
\usepackage{color}
\usepackage{soul}
\usepackage{marginnote}
\usepackage[T1]{fontenc}  %Gives you pipes for minor flags
\usepackage{makecell}  %For metrics table
%% If you want to create your own macros, you can do so
%% using \newcommand. Your macros should appear before
%% the \begin{document} command.
%\usepackage{multirow}
% \newcommand{\spcell}[2][c]{
%   \begin{tabular}[#1]{@{}l@{}}#2\end{tabular}}  %Creates line breaks in tables with left justification. 


\newcommand{\vdag}{(v)^\dagger}
\newcommand\aastex{AAS\TeX}
\newcommand\latex{La\TeX}
\newcommand\Kepler{\textit{Kepler}}
\newcommand\red{\textcolor{red}}
\newcommand\blue{\textcolor{blue}}
%% You can insert a short comment on the title page using the command below.
%\watermark{Fifth Draft. \today}
%%
%% If you wish, you may supply running head information, although
%% this information may be modified by the editorial offices.
%%\shorttitle{\aastex sample article}

%\shortauthors{Thompson et al.}


\begin{document}
%% You can add a light gray and diagonal water-mark to the first page
%% with this command:
%%\watermark{\today}

\title{Planetary Candidates Observed by \Kepler. VIII.\\
A Fully Automated Catalog With Measured Completeness and Reliability\\Based on Data Release 25 }

%\author{Susan E. Thompson and others}
%\input{authors}
\author[0000-0001-7106-4683]{Susan E. Thompson}
\altaffiliation{a.k.a. Susan E. Mullally, email: smullally@stsci.edu}
\affiliation{\seti}
\affiliation{\nasa}
\affiliation{\stsci}

\author[0000-0003-1634-9672]{Jeffrey L. Coughlin}
\affiliation{\nasa}
\affiliation{\seti}

\author{Kelsey Hoffman}
\affiliation{\seti}

\author{Fergal Mullally}
\affiliation{\seti}
\affiliation{\nasa}
\affiliation{\orbital}

\author{Jessie L. Christiansen}
\affiliation{\nexsci}

\author{Christopher J. Burke}
\affiliation{\nasa}
\affiliation{\seti}
\affiliation{\mitadd}

\author{Steve Bryson}
\affiliation{\nasa}

\author{Natalie Batalha}
\affiliation{\nasa}

\author{Michael R. Haas}
\altaffiliation{NASA Ames Associate}
\affiliation{\nasa}


\author{Joseph Catanzarite}
\affiliation{\seti}
\affiliation{\nasa}

\author[0000-0002-5904-1865]{Jason F. Rowe}
\affiliation{\bishop}

\author{Geert Barentsen}
\affiliation{\bari}


\author{Douglas A. Caldwell}
\affiliation{\seti}
\affiliation{\nasa}

%----------

\author{Bruce D. Clarke}
\affiliation{\seti}
\affiliation{\nasa}

\author[0000-0002-4715-9460]{Jon M. Jenkins}
\affiliation{\nasa}

\author{Jie Li}
\affiliation{\seti}

\author[0000-0001-9911-7388]{David W. Latham}
\affiliation{\cfa}

\author{Jack J. Lissauer}
\affiliation{\nasa}

\author{Savita Mathur}
\affiliation{Space Science Institute, 4750 Walnut Street, Suite 205, Boulder, CO 80301, USA}

\author{Robert L. Morris}
\affiliation{\seti}
\affiliation{\nasa}

\author{Shawn E. Seader}
\affiliation{Rincon Research Corporation,101 N Wilmot Rd, Tucson, AZ 85711}

\author{Jeffrey C. Smith}
\affiliation{\seti}
\affiliation{\nasa}

\author{Todd C. Klaus}
\affiliation{\nasa}

\author{Joseph D. Twicken}
\affiliation{\seti}
\affiliation{\nasa}

\author{Jeffrey E. Van Cleve}
\affiliation{\seti}

\author{Bill Wohler}
\affiliation{\seti}
\affiliation{\nasa}

\author[0000-0001-9674-1564]{Rachel Akeson}
\affiliation{\nexsci}

\author[0000-0002-5741-3047]{David R. Ciardi}
\affiliation{\nexsci}

\author[0000-0001-9662-3496]{William D. Cochran}
\affiliation{McDonald Observatory and Department of Astronomy, University of Texas at Austin, Austin, TX 78712}

\author{Christopher E. Henze}
\affiliation{\nasa}

\author{Steve B. Howell}
\affiliation{\nasa}

\author{Daniel Huber}
\affiliation{Institute for Astronomy, University of Hawai`i, 2680 Woodlawn Drive, Honolulu, HI 96822, USA}
\affiliation{Sydney Institute for Astronomy (SIfA), School of Physics, University of Sydney, NSW 2006, Australia}
\affiliation{\seti}
\affiliation{\aarhus}

\author[0000-0002-1913-0281]{Andrej Pr\v sa}
\affiliation{Villanova University, Dept.~of Astrophysics and Planetary Science, 800 Lancaster Ave, Villanova PA 19085}

\author{Solange V. Ram\'{\i}rez}
\affiliation{\nexsci}

\author{Timothy D. Morton}
\affiliation{Department of Astrophysical Sciences, Princeton University, 4 Ivy Lane, Princeton, NJ 08544, USA}


\author[0000-0001-7139-2724]{Thomas Barclay}
\affiliation{\nasagoddard}

\author{Jennifer R. Campbell}
\affiliation{\nasa}
\affiliation{\wyle}

\author{William J. Chaplin}
\affiliation{School of Physics and Astronomy, University of Birmingham, Edgbaston, Birmingham B15 2TT, UK}
\affiliation{\aarhus}

\author[0000-0002-9003-484X]{David Charbonneau}
\affiliation{\cfa}

\author{J{\o}rgen Christensen-Dalsgaard}
\affiliation{\aarhus}

\author{Jessie L. Dotson}
\affiliation{\nasa}

\author{Laurance  Doyle}
\affiliation{Institute for the Metaphysics of Physics, Principia College, One Maybeck Place, Elsah, Illinois 62028}
\affiliation{\seti}


\author{Edward W. Dunham}
\affiliation{Lowell Observatory, 1400 W Mars Hill Rd, Flagstaff, AZ 86001}

\author[0000-0002-8985-8489]{Andrea K. Dupree}
\affiliation{\cfa}

\author[0000-0001-6545-639X]{Eric B. Ford}
\affiliation{\pennstate} 
\affiliation{\habworlds} 
\affiliation{Center for Astrostatistics, 525 Davey Laboratory, The Pennsylvania State University, University Park, PA, 16802, USA} 
\affiliation{Institute for CyberScience, The Pennsylvania State University}


\author{John C. Geary}
\affiliation{\cfa}

\author{Forrest R. Girouard}
\affiliation{Orbital Sciences Corporation, 2401 East El Segundo Boulevard, Suite 200, El Segundo, CA 90245, USA}
\affiliation{\nasa}


\author[0000-0002-0531-1073]{Howard Isaacson}
\affiliation{Dept. of Astronomy, UC Berkeley, Berkeley, CA 94720, USA}


\author{Hans Kjeldsen}
\affiliation{\aarhus}

%Where Dave Koch actually belongs


\author{Elisa V. Quintana}
\affiliation{\nasagoddard}

\author{Darin Ragozzine}
\affiliation{Brigham Young University, Department of Physics and Astronomy, N283 ESC, Provo, UT 84602, USA}

\author[0000-0003-1179-3125]{Megan Shabram}
\altaffiliation{NASA Postdoctoral Program Fellow, Administered by Universities Space Research Association}
\affiliation{\nasa}


\author{Avi Shporer}
\affiliation{Division of Geological and Planetary Sciences, California Institute of Technology, Pasadena, CA 91125, USA}



\author{Victor Silva Aguirre}
\affiliation{\aarhus}


\author{Jason H. Steffen}
\affiliation{University of Nevada, Las Vegas, 4505 S Maryland Pkwy, Las Vegas, NV 89154}

\author{Martin Still}
\affiliation{\bari}


\author{Peter Tenenbaum}
\affiliation{\seti}
\affiliation{\nasa}


\author{William F. Welsh}
\affiliation{Department of Astronomy, San Diego State University, 5500 Campanile Drive, San Diego, CA 92182-1221}

\author[0000-0003-2862-6278]{Angie Wolfgang}
\altaffiliation{\nsffellow}
\affiliation{\pennstate} 
\affiliation{\habworlds}

\author{Khadeejah A Zamudio}
\affiliation{\nasa}
\affiliation{\wyle}

\author{David G. Koch}
\altaffiliation{deceased}
\affiliation{\nasa}

\author{William J. Borucki}
\altaffiliation{NASA Ames Associate}
\affiliation{\nasa}


\begin{abstract}
We present the Kepler Object of Interest (KOI) catalog of transiting exoplanets based on searching four years of \Kepler{} time series photometry (Data Release 25, Q1--Q17). The catalog contains \nkoisdr{} KOIs of which 4034 are planet candidates with periods between 0.25 and 632~days. Of these candidates, 219 are new in this catalog and include two new candidates in multi-planet systems (KOI-82.06 and KOI-2926.05), and ten new high-reliability, terrestrial-size, habitable zone candidates. This catalog was created using a tool called the Robovetter which automatically vets the DR25 Threshold Crossing Events (TCEs) found by the \Kepler\ Pipeline \citep{Twicken2016}. Because of this automation, we were also able to vet simulated data sets and therefore measure how well the Robovetter separates those TCEs caused by noise from those caused by low signal-to-noise transits. Because of these measurements we fully expect that this catalog can be used to accurately calculate the frequency of planets out to \Kepler{'s} detection limit, which includes temperate, super-Earth size planets around GK dwarf stars in our Galaxy. This paper discusses the Robovetter and the metrics it uses to decide which TCEs are called planet candidates in the DR25 KOI catalog.  We also discuss the simulated transits, simulated systematic noise, and simulated astrophysical false positives created in order to characterize the properties of the final catalog. For orbital periods less than 100\,d the Robovetter completeness (the fraction of simulated transits that are determined to be planet candidates) across all observed stars  is greater than 85\%. For the same period range, the catalog reliability (the fraction of candidates that are not due to instrumental or stellar noise) is greater than 98\%.  However, for low signal-to-noise candidates found between 200 and 500 days, our measurements indicate that the Robovetter is 73.5\% complete and 37.2\% reliable across all searched stars (or 76.7\% complete and 50.5\% reliable when considering just the FGK dwarf stars). We describe how the measured completeness and reliability varies with period, signal-to-noise, number of transits, and stellar type.  Also, we discuss a value called the disposition score which provides an easy way to select a more reliable, albeit less complete, sample of candidates. The entire KOI catalog, the transit fits using Markov chain Monte Carlo methods, and all of the simulated data used to characterize this catalog are available at the NASA Exoplanet Archive.


\end{abstract}

\keywords{catalogs --- planetary systems --- planets and satellites: detection --- stars: statistics --- surveys --- techniques: photometric}

%INTRODUCTION
\section{Introduction}
\input{section-introduction.tex}


%TCE Description
\section{The Q1--Q17 DR25 TCEs}
\label{tcesec}
\input{section-dr25TCEs.tex}
\input{section-InjInvSS1Tces.tex}
\input{section-DVTransitFits.tex}

%The ROBOVETTER
\section{The Robovetter: Vetting Methods and Metrics}
\input{section-robovetter.tex}

\section{Calculating Completeness and Reliability}
\input{section-reliability-calc.tex}

%Tuning the Robovetter for Completeness and reliability
\section{Tuning the Robovetter for High Completeness and Reliability}
\input{section-tuning.tex}


%All the pieces that need to be brought together to make the catalog.
\section{Assembling the DR25 KOI Catalog}
\input{section-assembleCatalog.tex}

\subsection{KOI Transit Model Fits}
\input{section-MCMC.tex}

%Analysis of the Catalog
\section{Analysis of the DR25 KOI Catalog}

\input{section-catalogsummary.tex}
\input{section-CompAndReliability.tex}
\input{section-multis.tex}
\input{section-HabitableZone.tex}

\input{section-occurRateCalc}


\input{section-conclusions}


\acknowledgments
The authors would like to thank the anonymous referee for providing comments that improved the clarity and accuracy of this manuscript. 
This paper includes data collected by the \Kepler{} mission. The Kepler Mission was a PI-led Discovery Class Mission funded by the NASA Science Mission directorate. The authors acknowledge the efforts of the \Kepler{} Mission team for generating the many data products used to create the KOI catalog. These products were generated by the \Kepler{} Mission science pipeline through the efforts of the Kepler Science Operations Center and Science Office. The Kepler Mission is led by the project office at NASA Ames Research Center. Ball Aerospace built the Kepler photometer and spacecraft which is operated by the mission operations center at LASP.  
We acknowledge the Kepler Education and Outreach team for their efforts in making the results of this paper accessible to the public. We thank the many scientists who contributed to the \Kepler\ Mission over the years, including R. Gilliland, E. Furlan, J. Orosz and K. Col\'{o}n. We thank the managers and engineers who worked on \Kepler{} over the years, without whom we would not have had a successful \Kepler{} Mission. This research has made use of NASA's Astrophysics Data System. We thank GNU parallel for enabling rapid running of the Robovetter input metrics \citep{Tange2011a}. We thank P.P. Mullally for inspiring the names of certain algorithms. Thank you to \citet{Turbo-King2017} for a spirited discussion.
Some of the data products used in this paper are archived at the NASA Exoplanet Archive, which is operated by the California Institute of Technology, under contract with the National Aeronautics and Space Administration under the Exoplanet Exploration Program. Some of the data presented in this paper were obtained from the Mikulski Archive for Space Telescopes (MAST). STScI is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS5-26555. Support for MAST for non-HST data is provided by the NASA Office of Space Science via grant NNX09AF08G and by other grants and contracts.  J.F.R acknowledges support from NASA grant NNX14AB82G issued through the Kepler Participating Scientist Program. This research was undertaken, in part, thanks to funding from the Canada Research Chairs program. This research was enabled, in part, by support provided by Calcul Qu\'{e}bec (www.calculquebec.ca) and Compute Canada (www.computecanada.ca). 
D.H. and S.M. acknowledge support by the National Aeronautics and Space Administration under Grant NNX14AB92G issued through the Kepler Participating Scientist Program. J.L.C. is supported by NASA under award No. GRNASM99G000001. J.S. is supported by the NASA \Kepler\ Participating Scientist Program NNX16AK32G.  W.F.W. gratefully acknowledges support from NASA via the \Kepler{} Participating Scientist Program grant NNX14AB91G. V.S.A. acknowledges support from VILLUM FONDEN (research grant 10118).
Funding for the Stellar Astrophysics Centre is provided by The Danish National Research Foundation (Grant DNRF106). The research was supported by the ASTERISK project (ASTERoseismic Investigations with SONG and Kepler) funded by the European Research Council (Grant agreement no.: 267864).

\added{
\software{George \citep{Ambikasaran14}, Kepler Science Data Processing Pipeline (\url{https://github.com/nasa/kepler-pipeline}), Robovetter (\url{https://github.com/nasa/kepler-robovetter}), Marshall (\url{https://sourceforge.net/projects/marshall/}), Centroid Robovetter \citep{Mullally2017}, LPP Metric \citep{Thompson2015a}, Model-Shift Uniqueness Test \citep{Rowe2015cat}, Scipy package (\url{https://www.scipy.org}), Ephemeris Match (\url{https://github.com/JeffLCoughlin/EphemMatch}), Kepler: Kepler Transit Model Codebase Release, \url{https://doi.org/10.5281/zenodo.60297}}
}

%\input{RV-minorFlags}
\bibliographystyle{aasjournal}
\bibliography{References.bib,KSCI-Refs.bib}

%$ $  % This is necessary for clearpage to actually work
%\clearpage

\appendix
\twocolumngrid
\input{section-robovetterMetrics.tex}
\input{section-minorflags.tex}

\clearpage
%\tableofcontents

\listofchanges

\end{document}


