\label{s:mcmc}

Each KOI, whether from a previous catalog or new to the DR25 catalog, were fit with a transit model in a consistent manner. The model fitting was performed in a similar manner as described in \S5 of \citet{Rowe2015cat}. The basic steps to do the model fits start with the DR25 Q1-Q17 PDC photometry from MAST\footnote{https://archive/stsci.edu.kepler/}. The photometry was detrended using a polynomial filter as described in \S4 of \citet{Rowe2014}. A transit model based on \citet{Mandel2002} was utilized in the fitting, assuming circular orbits and using quadratic limb darkening \citep{Claret2011} calculated for updated stellar parameters \citep{Mathur2017ApJS}. The transit model fits were obtained with least-squares minimization using a Levenberg-Marquardt routine \citep{More1980}. Transit Timing Variations (TTVs) are included in the model fit when necessary, the calculation of TTVs follows the procedure described in \S4.2 of \citet{Rowe2014}. The 296 KOIs with TTVs and the TTV measurements of each transit are listed in Table~\ref{t:ttv}. The uncertainties for the fitted parameters were calculated using a Markov-chain Monte Carlo (MCMC) method \citep{Ford2005AJ} with 2$\times 10^{5}$ chains calculated for each fit. In order to calculate the posterior distribution the first 20\% of each chain was discarded. The transit model fit parameters were combined with the stellar parameters and error bars \citep{Mathur2017ApJS} in order to produce the reported planetary fits. The MCMC chains are all available at the Exoplanet Archive and are documented in \citet{Hoffman2017}. 

The planet parameters are from the least-squares model fits and the errors from the MCMC calculations. Note that not all KOIs could be successfully modelled, resulting in three different fit types: "LS+MCMC", "LS", and "none". In the case of "LS+MCMC" the KOIs were fully modelled with both a least-squares model fit and the MCMC calculations were completed to provide error bars. In the cases where the MCMC calculations did not converge but there is a model fit, the least-square (LS) parameters are available without uncertainties (LS fit-type). In the final case, where a KOI could not be modelled, as in cases where the transit event was not found in the detrending used by the MCMC fits; only the period, epoch and duration of the federated TCE are reported and the fit type is listed as ``none".

\input{ttv-short.tex}