\begin{deluxetable*}{lllll}
\tablecolumns{11}
\tabletypesize{\scriptsize}
\tablewidth{\linewidth}
\tablecaption{Summary of the DR25 Robovetter tests.}
\tablehead{Test Name & Section & \spcell{Major\\Flags} & \spcell{Minor\\Flags} & \spcell{Brief\\Description} }

Is Secondary  & \ref{s:issecond} & \spcell{NT\\SS}  & IS\_SEC\_TCE & The TCE is a secondary eclipse\\
\hline\\
LPP Metric    & \ref{s:lpp}      & NT   & \spcell{LPP\_DV\\LPP\_ALT} & The folded event is transit-shaped. \\
\hline\\
SWEET NTL     & \ref{s:sweetntl} & NT   &  SWEET\_NTL                & The folded event is sinusoidal. \\[2pt]
\hline\\
TCE CHASES    &  \ref{s:tcechases} & NT & ALL\_TRANS\_CHASES         & The transit detection statistic is unique. \\[2pt]
\hline\\
MS$_1$        &   \ref{s:ms}       & NT & \spcell{MOD\_NONUNIQ\_DV\\MOD\_NONUNIQ\_ALT} & The transit is not significant compared to red noise.  \\
\hline\\
MS$_2$        &  \ref{s:ms}        & NT & \spcell{MOD\_TER\_DV\\MOD\_TER\_ALT} & Other phases are significant in the folded light curve. \\
\hline\\
MS$_3$        & \ref{s:ms}         & NT & \spcell{MOD\_POS\_DV\\MOD\_POS\_ALT} & A positive going event is significant in the folded light curve.  \\
\hline\\
Max SES to MES &  \ref{s:sesmes}  & NT & INCONSISTENT\_TRANS          & TCE is dominated by a single transit. \\[2pt]
\hline\\
Same Period    & \ref{s:sameperiod} & NT &  SAME\_NTL\_PERIOD       & TCE has the same period as a previous not-transit-like TCE. \\[2pt]
\hline\\
Individual Transits & \ref{s:indivtrans} & NT & INDIV\_TRANS\_ & Three transits remain whose recalculated MES is $\geq$7.1.\\[2pt]
\hspace{2em}Rubble         & \ref{s:rubble}    & - & INDIV\_TRANS\_RUBBLE    & Transit does not contain enough cadences.\\
\hspace{2em}Marshall       & \ref{s:marshall}   & - & INDIV\_TRANS\_MARSHALL  & Transit more closely matches a known artifact. \\
\hspace{2em}Chases         & \ref{s:chases}     & - & INDIV\_TRANS\_CHASES    & Transit event is not uniquely significant.\\
\hspace{2em}Skye           & \ref{s:skye}       & - & INDIV\_TRANS\_SKYE      & Transit time is correlated with other TCE transits. \\
\hspace{2em}Zuma           & \ref{s:zuma}       & - & INDIV\_TRANS\_ZUMA      & Transit is consistent with an increase in flux.\\
\hspace{2em}Tracker        & \ref{s:tracker}   & - & INDIV\_TRANS\_TRACKER   & Fitted transit time does not match discovery transit time.\\
\hline\\
Gapped Transits& \ref{s:rocky}     & NT & TRANS\_GAPPED          &  The fraction of transits labeled as bad is large.\\
\hline\\
MS Secondary& \ref{s:second} & SS & \spcell{MOD\_SEC\_DV\\MOD\_SEC\_ALT} & A significant secondary event is detected. \\
\hline\\
Secondary TCE& \ref{s:secondTce} & SS & HAS\_SEC\_TCE & A subsequent TCE on the same star is the secondary.\\
\hline\\
Odd Even &  \ref{s:oddeven} & SS & \spcell{DEPTH\_ODDEVEN\_DV\\DEPTH\_ODDEVEN\_ALT} &  The depth of odd and even transits are different.\\
\hline\\
SWEET EB & \ref{s:sweeteb} & SS & SWEET\_EB & Out-of-phase tidal deformation was detected.\\
\hline\\
V Shape Metric & \ref{s:shapemetric} & SS & DEEP\_V\_SHAPE & The transit is v-shaped.\\
\hline\\
Resolved Offset & \ref{s:centroidrv} & CO & CENT\_RESOLVED\_OFFSET & The transit occurs on a spatially resolved target.\\
\hline\\
Unresolved Offset & \ref{s:centroidrv} & CO & CENT\_UNRESOLVED\_OFFSET & A shift in the centroid position occurs during transit.\\
\hline\\
Ghost Diagnostic & \ref{s:ghost} & CO & HALO\_GHOST & The transit strength in the halo pixels is too high.\\
\hline\\
Ephemeris Match & \ref{s:ephemmatch} & EC & EPHEM\_MATCH & The ephemeris matches that of another source.

\enddata
\tablecomments{\textbf{Do we need to include the two tests that cause things to PASS here? I also don't see a description of them in the Robovetter Appendix.} }
\label{t:metrics}
\end{deluxetable*}